Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-04-04 sections/4gluing_alt.tex
Small addition to 4.

\section{Collar-gluings and Disk Algebras}\label{ch:gluing_disk_alg}

@@

We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar-gluings and sequential colimits. Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits.

@@

Considering \Cref{thm:decom_strat_man} together with the statements of \Cref{cor:disk_alg=falg} (or \Cref{thm:disk_alg=lcfa} in the locally constant case), together with the above \Cref{prop:fa_seq_col}, we have an algorithm of how to compute the $\infty$-category of factorization algebras on any manifold if we know it on the basics. In other words, the theory of (locally constant) factorization algebras is fully determined by the assignment
%
\begin{equation}
    U \mapsto \falg_U (\catC),
\end{equation}
%
for each basic $U \in \bsc$.

After a simplification down to disks, in the locally constant case , lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:

\begin{conjecture}
    The theory of locally constant factorization algebras is fully determined, using factorization homology, by the data of a functor
    %
    \begin{equation}
        \bsc \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
    \end{equation}
    %
    which to each basic $U$ attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
\end{conjecture}

>>>>

\section{Collar-gluings and Factorization Algebras}\label{ch:gluing_disk_alg}

@@

We know from \Cref{thm:decom_strat_man} that any manifold can be constructed from basics by iterated collar-gluings and sequential colimits. Having described what happens to a locally constant factorization algebras under collar-gluings of manifolds, we now turn to sequential colimits. {\color{red} The gluing result has an ordinary (nonhomotopy) limit. Is this also the output of the (co)bar construction?}

@@

Considering \Cref{thm:decom_strat_man} together with the statements of \Cref{cor:disk_alg=falg} (or \Cref{thm:disk_alg=lcfa} in the locally constant case), together with the above \Cref{prop:fa_seq_col}, we have an algorithm of how to compute the $\infty$-category of factorization algebras on any manifold if we know it on the basics. In other words, the theory of (locally constant) factorization algebras is fully determined by the assignment
%
\begin{equation}
    U \mapsto \falg_U (\catC),
\end{equation}
%
for each disk $U \in \bsc$.

After a simplification down to disks, in the locally constant case, lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:

%\begin{conjecture}
%    The theory of factorization algebras is fully determined, using factorization homology, by the data of a functor
%    %
%    \begin{equation}
%        \mathsf{Bsc} \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
%    \end{equation}
%    %
%    In the locally constant case, we can even say that to each basic $U$ this functor attaches the $\infty$-category $\mathsf{Fun}^{\otimes} (\disk(\mathsf{B}_U), \catC)$ of disk algebras with $\mathsf{B}_U$ structure, where $\mathsf{B}_U$ is the sieve poset whose maximal element is $U$.
%\end{conjecture}

%\begin{remark}
%    The $\infty$-category of basics $\mathsf{B}_{U}$ for our purposes provides a kind of generalization of framing, which makes calculation easier.
%\end{remark}

### 2024-04-04 sections/5classification.tex
Small addition to 4.

\begin{observation}\label{obs:explore_D*}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \Cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras). The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$. All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).

@@

\begin{proof}
    From \Cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^n_*} (\catC) \simeq \alg{\mathscr{D}_*} (\catC),
    \end{equation}
    %
    where we used the notation from \Cref{obs:explore_D*}. Specializing \Cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n}_A (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\mathscr{D}_*} (\catC) \arrow[d] \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
            * \arrow[r, "\{A\}"] & \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
    %
    The right square obviously commutes by construction. Since, by definition, $\mathsf{Mod}^{\mathbb{E}_n} (\catC)$ is fibered over $\alg{\mathbb{E}_n} (\catC)$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A (\catC)$ for $A$ an $\mathbb{E}_n$-algebra, the above diagram gives exactly the desired statement.
\end{proof}

>>>>

\begin{observation}\label{obs:explore_D*}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \Cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras). The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$. %All of these facts are partially an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$).

@@

\begin{proof}
    From \cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^n_*} (\catC) \simeq \alg{\mathscr{D}_*} (\catC),
    \end{equation}
    %
    where we used the notation from \Cref{obs:explore_D*}. Specializing \Cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n}_A (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\mathscr{D}_*} (\catC) \arrow[d] \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
            * \arrow[r, "\{A\}"] & \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
    %
    The right square obviously commutes by construction. Since, by definition, $\mathsf{Mod}^{\mathbb{E}_n} (\catC)$ is fibered over $\alg{\mathbb{E}_n} (\catC)$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A (\catC)$ for $A$ an $\mathbb{E}_n$-algebra, the above diagram gives exactly the desired statement.
\end{proof}
